Drought-sensitive trees survive on deep-water access in a tropical forest community

### 2020-08-29 manuscript.rmd
added vpd model coefficients dynamically

\
As VPD may have a non-linear relationship with growth, we fitted a polynomial curve between mean daily values by month of gross primary productivity (gC m^2^ day^-1^) and VPD we collected from the eddy flux tower (kPa; $\bar{GPP} = -18.8VPD^2 + 14.5VPD + 5.02 + error = StdVPD$; 2012-2017; Fig. S\@ref(fig:gpp-vpd)) and used standardized $\bar{GPP}$ to represent the impact of VPD on growth (hereafter, $StdVPD$; range 0-1) in Eqs. \@ref(eq:M2), \@ref(eq:M3) \@ref(eq:M5) and \@ref(eq:M6). Due to the coincidence of higher temperature, higher radiation, and lower humidity during the dry season at our study site, the impact of VPD may as well be a combined impact of temperature, humidity, and radiation.

>>>>

\
As VPD may have a non-linear relationship with growth, we fitted a polynomial curve between mean daily values by month of gross primary productivity (gC m^2^ day^-1^) we collected from the eddy flux tower and VPD (kPa; $\bar{GPP} = `r vpd.cf[1]` + `r vpd.cf[2]`VPD + `r vpd.cf[3]`VPD^2 + error = StdVPD$; 2012-2017; Fig. S\@ref(fig:gpp-vpd)) and used standardized $\bar{GPP}$ to represent the impact of VPD on growth (hereafter, $StdVPD$; range 0-1) in Eqs. \@ref(eq:M2), \@ref(eq:M3) \@ref(eq:M5) and \@ref(eq:M6). Due to the coincidence of higher temperature, higher radiation, and lower humidity during the dry season at our study site, the impact of VPD may as well be a combined impact of temperature, humidity, and radiation.
